---
title: "R-HW2-AbinithaShivakumar"
author: "Abinitha Shivakumar"
date: "October 30, 2018"
output: html_document
---

Answer 1:
```{r}
library(tidyverse)
library(gains)
library(leaps)
library(caret)

SystemAdministrators <- read.csv("SystemAdministrators.csv", header = TRUE)
head(SystemAdministrators)
View(SystemAdministrators)
set.seed(1)

ggplot(SystemAdministrators, aes(x=Experience, y=Training, color= Completed.task)) + geom_point(size = 3, shape = 21) + labs(title = 'Training vs Experience', y='Training credits', x='Experience')
```

The number of years of experience is a better predictor than the training credits as we see from the plot that most of the tasks which are not completed have less than 8 years of experience. We can observe that it is the same for 4,6 and 8 training credits. We can infer that training credits have lesser impact on completion of the task as compared to experience.


Answer 2:

```{r}

logit.reg <- glm(Completed.task ~ ., data = SystemAdministrators, family = "binomial") 
options(scipen=999)
summary(logit.reg)

prediction=predict(logit.reg, SystemAdministrators[,-3],type='response')
prediction = ifelse(prediction > 0.5, 1, 0)
prediction

#confusion matrix
confusionmatrix = table(SystemAdministrators[, 3], prediction)
confusionmatrix

```

Answer continued : 5 - incorrect and 15 completed, the percentage of programmers classified incorrectly as failing to complete the task is:

5/15 * 100 = 33.33%



Answer 3:
p=0.6
odds=p/1-p
odds=0.6/0.4
odds=1.5
log(odds)=B0+ B1x1 + B2x2
log(1.5)= -10.9813 + 1.1269 (experience)+0.1805 (Traininig)
0.1761=-10.9813 + 1.1269(experience)+0.1805 (6)
experience=(0.1761+10.9813-1.083)/1.1269
experience=8.94











